Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2020-03-11 response_to_review_SOLA-D-20-00015_v1.txt

-----------------------------------------------------------------------------------------
Q8. The introduction does not have many references to works beyond DEMT and AWSoM. The 2nd paragraph of the introduction offers a chance to remedy this, where you discuss the quiet-Sun corona. I know there are very few works that address the quiet corona in the context of DEM analysis, but you can reference https://www.aanda.org/articles/aa/full_html/2014/04/aa23054-13/aa23054-13.html. You can also mention https://iopscience.iop.org/article/10.1088/0004-637X/795/2/111 here (although you do reference this paper in more detail in the discussion). Another relevant paper which can be referenced, with DEM analysis of a large amount of quiet coronal data over long time periods, is https://advances.sciencemag.org/content/3/7/e1602056 .

A8. We agree it is important to expand the references in the article to other studies of the quiet Sun. As you mention, we do refer to Hahn & Savin (2014) alreadyin the discussion. In the Introduction, we included now the other references you provided, as well as another one (new text in red).

### 2020-03-11 lloveras_2020_v2.tex
Albert está trabajando en esto, no tocar todavía, gracias.

@@

{Combining the DEMT and AWSoM models, we carry out a detailed \edit{quantitative} analysis of two target rotations. We selected Carrington rotation} (CR)-2082 (2009, 05 April through 03 May) during the Solar Cycle (SC) 23/24 minimum, and CR-2208 (2018, 02 September through 29 September) during {the end of the declining} phase of SC 24. {In the case of CR-2082, the DEMT analysis is based on data} taken by the \textit{Extreme UltraViolet Imager Behind} {(EUVI-B: \citealt{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} {(STEREO), while the AWSoM model uses the synoptic magnetogram provided by the Global Oscillation Network Group (GONG: \citealt{gong}). In the case of CR-2208, the DEMT analysis is based \edit{on} data taken} by the \textit{Atmospheric Imaging Assembly instrument} {(AIA: \citealt{lemen_2012})} on board the \textit{Solar Dynamics Observatory} {(SDO), while the AWSoM model uses the magnetogram provide by the Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG model.}

@@

\edit{As the LDEM describes the temperature distribution of the plasma in a specific voxel, it does not deal with different large scale structures, as it may be the case for the DEM describing the plasma along a full LOS. As a result, LDEMs are usually successfully modeled with simpler profiles (such as Gaussian) than those returned by DEM studies constrained by LOS-integrated intensities. Parametric techniques are also used for DEM analysis of narrowband images, such as in the works by \citet{aschwanden_2011,plowman_2013,delzanna_2013}. Other methods applied to DEM analysis of narrow band images include Monte Carlo Markov Chain (MCMC) techniques \citep{schmeltz_2016}, regularized inversion techniques \citep{hannah_2012}, and iterative solvers \citep{pickering_2019,morgan_2019} that use the known TRFs of all filters as a functional base. The latter work in particular, introduces a fast iterative solver named SITES, which can easily be adapted for its use in DEMT. We will explore this in the future.}

>>>>

\edit{Non-tomographic studies of localized regions of the quiet-Sun corona have been carried out by means of DEM analysis. \citet{mackovjak_2014} used regularized inversion techniques to study characteristic temperatures in the quiet-Sun. \citet{lopez_2019} used a parametric method to study EUV dimmings after coronal mass ejections (CMEs) in order to estimate the coronal mass evacuated by the events. At a global scale, DEM analysis has been used by \citet{morgan_2017} to characterize the evolution of the temperature of the quiet-Sun corona during most of solar cycle (SC) 24.}

@@

{Combining the DEMT and AWSoM models, we carry out a detailed \edit{quantitative} analysis of two target rotations. We selected Carrington rotation} (CR)-2082 (2009, 05 April through 03 May) during the SC 23/24 minimum, and CR-2208 (2018, 02 September through 29 September) during {the end of the declining} phase of SC 24. {In the case of CR-2082, the DEMT analysis is based on data} taken by the \textit{Extreme UltraViolet Imager Behind} {(EUVI-B: \citealt{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} {(STEREO), while the AWSoM model uses the synoptic magnetogram provided by the Global Oscillation Network Group (GONG: \citealt{gong}). In the case of CR-2208, the DEMT analysis is based \edit{on} data taken} by the \textit{Atmospheric Imaging Assembly instrument} {(AIA: \citealt{lemen_2012})} on board the \textit{Solar Dynamics Observatory} {(SDO), while the AWSoM model uses the magnetogram provide by the Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG model.}

@@

\edit{As the LDEM describes the temperature distribution of the plasma in a specific voxel, it does not deal with different large scale structures, as it may be the case for the DEM describing the plasma along a full LOS. As a result, LDEMs are usually successfully modeled with simpler profiles (such as Gaussian) than those returned by DEM studies constrained by LOS-integrated intensities. Parametric techniques are also used for DEM analysis of narrowband images, such as in the works by \citet{aschwanden_2011,plowman_2013,delzanna_2013}. Other methods applied to DEM analysis of narrow band images include Monte Carlo Markov Chain (MCMC) techniques \citep{schmeltz_2016}, regularized inversion techniques \citep{hannah_2012}, and iterative solvers \citep{pickering_2019,morgan_2019} that use the known TRFs of all filters as a functional base. The latter work in particular, introduced a fast iterative solver named SITES, which can easily be adapted for its use in DEMT. We will explore this in the future and compare results with those provided by our parametric technique.}
